---
title: "eds212-day5"
author: "IMS"
format: html
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

```{r}
#| message: false
# load libraries ----
library(tidyverse)

```

Try using `head()`, `tail()`, and `dim()` on the `dplyr::starwars` data frame:

```{r}
#| include: false
# do some data exploration on the starwars df ----

head(starwars)
tail(starwars)
dim(starwars)
```

- Create a ggplot (scatter plot) of character `mass` (y-axis) and `height` (x-axis)
- Update the color of the points so that color changes based on the value of `mass`

```{r}
#| fig-cap: "This is my figure caption"
#| fig-alt: "This is some alt text"
ggplot(starwars, mapping = aes(x=height, y=mass, color=mass))+
  geom_point() + 
  labs(x="Height (cm)", 
       y="Mass (kg)",
       title = "Here is my title")
```

- Create a histogram of character heights
- Update the fill color (`fill`) to purple and the outside border line (`color`) of each histogram bin to orange
- Update your code chunk options so that only your code and output graph appear in the rendered doc
- Update the axis labels

```{r}
#| fig-cap: "This is my figure caption"
#| fig-alt: "This is some alt text"
ggplot(starwars, mapping = aes(x=height))+
  geom_histogram(fill="purple", color="orange") + 
  labs(x="Height (cm)", 
       y="Count")
```

`df$col_name`

```{r}
sw_height_mean <-round(mean(starwars$height, na.rm=TRUE), 3)
```

The mean height of all starwars characters is `r sw_height_mean`

